---
title: "Data structures Day2"
output: html_document
editor_options: 
  chunk_output_type: console
---
## vectors
Vector 1 Dimension  homogenous 
List   1 D      hetergenous
matrix  2D          homo
data frame   2D     heter 
Array        nD 


1. how to create vector
```{r}
(grand_slam_win <- c(9, 15, 5, 12, 18))

```


it can be have combined vector
```{r}
(grand_slam_win <- c(9, c(15, 5), 12, 18))

```
What inside of vector
```{r}
a=c(1,2,3)
a2=c(1L,2L,3L)
b=c("a","b")
```

```{r}
typeof(a)
typeof(a2)
typeof(b)
```

Coercion

logical<integer<numeric<charact
if means smaller things will transfrom to big such as 
```{r}
c("a",1)

```

Subsetting

```{r}
(a=c(1,20,3,40))
a[2]
a[c(2,1,4)]
a[-1]
a[-c(1,2)]
a[-c(1,2)][-2]
```

```{r}
(a=c(1,20,3,40))
a[c(F,F,F,T)]
a>10
a[a>10]
```
Attributes 
Adding labels to your vector

```{r}
(grand_slam_win <- c("Andy Murray" = 9, "Rafael Nadal" = 15, 
                   "Stan Wawrinka" = 5, "Novak Djokovic" = 12, 
                   "Roger Federer" = 18))

grand_slam_win["Roger Federer"]
grand_slam_win[4]
```

Useful function of vectors

```{r}
length(grand_slam_win)
mean(grand_slam_win)
sum(grand_slam_win)
sort(grand_slam_win,decreasing = T) 
order(grand_slam_win)
grand_slam_win[order(grand_slam_win)]

```
Creat sequence
```{r}
1:6
seq(from=12,to=23.5,length.out = 5)
```


```{r}
(today=Sys.Date())
(three_months_ago <- seq(today, length = 2, by = "-3 months")[2])
library(quantmod)
getSymbols("AAPL", from = three_months_ago, to = today)
candleChart(AAPL, theme = 'white', type = 'candles')
AAPL_returns <- na.omit(ClCl(AAPL))

View(AAPL)
```

Excess Kurtosis 
test the Kurtosis (how the data distribution)

```{r}
mean(AAPL_returns)
median(AAPL_returns)
mu <- mean(AAPL_returns)
(k <- mean((AAPL_returns - mu)^4)/(mean((AAPL_returns - mu)^2))^2 - 3)
```


Matrice
```{r}
(mat <- matrix(1:12, ncol = 4,  nrow = 3))
mat[2,2]
mat[,2]
mat[-2,]
```

```{r}
players <- c("Andy Murray", "Rafael Nadal", "Stan Wawrinka", 
             "Novak Djokovic", "Roger Federer")
grand_slam_win <- c(9, 15, 5, 12, 18)
win_percentage <- c(78.07, 82.48, 63.96, 82.77, 81.80)
(mat <- cbind(grand_slam_win, win_percentage))
dimnames(mat)
dimnames(mat)[[1]]=players
rownames(mat) <- players
mat
mat[c("Andy Murray", "Rafael Nadal"),"grand_slam_win"]
mat[1:3,]
```

Transpose = change the tow as clone

```{r}
(A <- matrix(1:8, 4, 2))
t(A)
dim(A)
nrow(A)
length(A)
```

matrice calculate
* just element times element
```{r}
(B=matrix(1:4,2,2))
B*B
B%*%B
B_inv=solve(B)
?solve
```

An example of risk
Asumption is variation of store is smallest 

```{r}
# Load quantmod
library(quantmod)

# Download data
today <- Sys.Date()
five_years_ago <- seq(today, length = 2, by = "-5 year")[2]
getSymbols("AAPL", from = five_years_ago, to = today)
getSymbols("NFLX", from = five_years_ago, to = today)

# Compute returns
Ra <- na.omit(ClCl(AAPL))
Rn <- na.omit(ClCl(NFLX)) 

# Estimation of mu and Sigma
Sigma <- cov(cbind(Ra, Rn))
mu <- c(mean(Ra), mean(Rn))

# Compute omega^*
omega_star <- (Sigma[2, 2] - Sigma[1, 2])/(Sigma[1, 1] + Sigma[2, 2] - 2*Sigma[1, 2])
omega_star

# Compute investment expected value and variance
mu_investment <- omega_star*mu[1] + (1 - omega_star)*mu[2]
var_investment <- omega_star^2*Sigma[1,1] + (1 - omega_star)^2*Sigma[2,2] + 
  2*omega_star*(1 - omega_star)*Sigma[1,2]
```


```{r}
investment_summary <- matrix(NA, 2, 3)
dimnames(investment_summary)[[1]] <- c("Expected value", "Variance")
dimnames(investment_summary)[[2]] <- c("Apple", "Netflix", "Investment")
investment_summary[1, ] <- c(mu, mu_investment)
investment_summary[2, ] <- c(diag(Sigma), var_investment)
?kable
knitr::kable(investment_summary)
```

Graph example
```{r}

```

List


```{r}
# List elements
num_vec <- c(188, 140)
char_vec <- c("Height", "Weight", "Length")
logic_vec <- rep(TRUE, 8)
my_mat <- matrix(0, nrow = 5, ncol = 5)

# List initialization 
(my_list <- list(num_vec, char_vec, logic_vec, my_mat))

# List initialization with custom names 
(my_list <- list(number = num_vec, character = char_vec, 
                 logic = logic_vec, matrix = my_mat))
```


Dataframe----- use most
Use it when you want to save different things in one place 
```{r}
### Creation

players <- c("Andy Murray", "Rafael Nadal", "Stan Wawrinka", 
             "Novak Djokovic", "Roger Federer")

grand_slam_win <- c(9, 15, 5, 12, 18)

date_of_birth <- c("15 May 1987", "3 June 1986", "28 March 1985", 
                  "22 May 1987", "8 August 1981")

country <- c("Great Britain", "Spain", "Switzerland", 
            "Serbia", "Switzerland")
ATP_ranking <- c(1, 2, 3, 4, 5)

prize_money <- c(60449649, 85920132, 30577981, 109447408, 104445185)

tennis <- data.frame(date_of_birth, grand_slam_win, country, 
                    ATP_ranking, prize_money)
View(tennis)
dimnames(tennis)[[1]] <- players
tennis[1,4]

```
##Control Structure

```{r}
a=3
b=4
a>b
a<=b
#! means take the opposite
!(a>b)
#|| means or  if only have one is ture then the answer will be ture. ONly need one ture to be ture
!(a<b)||a>0
#&& means and all ture then is ture. 
!(a<b)&&a>0

```

```{r}
a=1:13
a>2
sum(a>2)
#F=0,T=1
a>4
a<10
a>4&&a<10
a>4 & a<10
a[a>4 & a<10]
```
if
```{r}
a=2
if (a>0){a=4
}
a
```

```{r}
a=10
#%% means the remain
3%%2

if (a%%2==0){print(paste(a,"is an even number"))
}

```




if else

you can have more else, they have orders
```{r}
x=21
if (x %% 2 == 0){
  print(paste(x, "is an even number"))
}else{
  print(paste(x, "is an odd number"))
}

```

For loop
repreat all the posible value in for(for is how many time it will loop)
```{r}
for (number in 1:6){
  print(number)
}

a=1
for (number in 1:6){
  a=a+1
}
a
```

```{r}
a=1:6
sum(a)
n=length(a)
mysum=0
for (i in 1:n) {mysum=a[i]+mysum
  
}
mysum
```
